A framework for mentored data science research projects

### 2019-10-26 Rmd/jse-2019-ms.Rmd
updated ms & bib file

---
title: 'Making Sense of Tweets: A framework for individualized student research projects'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
lastmod: "`r lubridate::now()`"
bibliography: jse.bib
output: html_document
---

@@

## Discussion

>>>>

---
title: 'A framework for mentored data science research projects'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
output: bookdown::html_document2
---

Last modified: `r params$lastmod`

@@

### 2019-10-26 Rmd/methods.Rmd
updated ms & bib file

@@

We mentored two data science researchers in the last year of undergraduate study in statistics at University of Wisconsin-Madison. Both students developed novel research questions, collected observational data, analyzed data, and interpreted results.

>>>>

We designed and used a framework for mentored undergraduate data science research projects with big data. Our framework draws heavily on ideas in @nolan2010computing. Specifically, we incorporate the three key aspects that @nolan2010computing identified:

1. broaden statistical computing to include emerging areas
1. deepen computational reasoning skills
1. combine computational topics with data analysis in the practice of statistics

Our mentored research framework begins with brainstorming research ideas based on the student's interests. From there, we (mentor and student together) formulate the most promising ideas into scientific hypotheses. For the most appealing hypotheses, we encourage the student to translate the scientific question into a statistical question that may be addressed with data analysis.

@@
